Exception Handling Bug Hazards in Android

### 2015-10-09 SPRINGER_JOURNAL/msr_journal.tex
fixing typos

\begin{abstract}
This paper reports two studies:  a repository mining study whose goal was to identify 
exception handling bug hazards in Android apps; and an exploratory survey study - whose goal
was to assess the perspectives of developers concerning such bug hazards.
The repository mining study mined the exception stack traces embedded on 
159,048 issues reported on Android projects hosted in GitHub (482 projs.) 
and Googlecode (157 projs.).  Overall 6,005 exception stack traces were extracted, 
and analyzed in combination with source code and bytecode analysis. 
Some bug hazards were consistently detected such as:  unexpected exception wrappings 
(e.g., Errors being wrapped in checked exceptions), and NullPointerExeptions 
as the major cause of reported crashes - reported in 
28\% of all mined stack traces found in about 50\% of all analyzed projects. 
Finally, a survey was applied to some developers 
involved on some of the GitHub Android projects analyzed in our study 
and their perspective about the bug hazards and 
how they deal with them was assessed and discussed.

@@

%Q1Q2_new.png
\begin{figure} \centering \includegraphics[scale=0.38]{charts/expertise_new.png}
\caption{Developers expertise in Java and Android development.}
\label{fig:devexpertise}
\end{figure}

@@

\begin{figure} \centering \includegraphics[scale=0.58]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:often}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.60]{charts/yes_no_new2.png}
\caption{Summary of some survey question answers. }
\label{fig:allquest}
\end{figure}

@@

Developers were also asked to rank the main causes of crashes. Approximately 68\% of the respondents ranked the exceptions signaled by programming logic mistakes, e.g. NullPointerExceptions, as the Top 1 and Top 2 cause of crashes, as illustrated in Figure~\ref{fig:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52.0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.60]{charts/ranking.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}

@@

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

>>>>

\begin{abstract}
This paper reports two studies:  a repository mining study whose goal was to identify 
exception handling bug hazards in Android apps; and an survey-based study whose goal
was to assess the perspectives of developers concerning such bug hazards.
The repository mining study mined the exception stack traces embedded on 
159,048 issues reported on Android projects hosted in GitHub (482 projs.) 
and Googlecode (157 projs.).  Overall 6,005 exception stack traces were extracted, 
and analyzed in combination with source code and bytecode analysis. 
Some bug hazards were consistently detected such as:  unexpected exception wrappings 
(e.g., Errors being wrapped in checked exceptions), and NullPointerExeptions 
as the major cause of reported crashes - reported in 
28\% of all mined stack traces found in about 50\% of all analyzed projects. 
Finally, a survey was applied to some developers 
involved on some of the GitHub Android projects analyzed in our study 
and their perspective about the bug hazards and 
how they deal with them was assessed and discussed.

@@

%Q1Q2_new.png
\begin{figure} \centering \includegraphics[scale=0.38]{expertise_new.png}
\caption{Developers expertise in Java and Android development.}
\label{fig:devexpertise}
\end{figure}

@@

\begin{figure} \centering \includegraphics[scale=0.58]{agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:often}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.60]{yes_no_new2.png}
\caption{Summary of some survey question answers. }
\label{fig:allquest}
\end{figure}

@@

Developers were also asked to rank the main causes of crashes. Approximately 68\% of the respondents ranked the exceptions signaled by programming logic mistakes, e.g. NullPointerExceptions, as the Top 1 and Top 2 cause of crashes, as illustrated in Figure~\ref{fig:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52.0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.60]{ranking.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}

@@

\begin{acknowledgements}
This work is partially supported by INES, funded by CNPq and
FACEPE, grants 573964/2008-4 and APQ-1037-1.03/08.
\end{acknowledgements}
